BIP Architectures and Open pNets

### 2019-02-01 2018-Arch-pNets/arch-pNets.tex
abstract et keyword

\begin{abstract}
  We extend the theory of architectures with a general
  mechanism for handling various types of data transfer.  We
  encode this extended model into the open pNet semantic
  model and show how this encoding can be used to verify
  that an architecture does, indeed, enforce its
  characteristic property.

\keywords{}
\end{abstract}

>>>>

\begin{abstract}
This paper provides a solution for the compositional design of systems and their verification. The approach taken consists in designing architectural elements that guaranty safety properties and composing them to build a safe system.

More precisely, this article provides a theory of architectures based on the BIP system.
It extends preliminary work in this domain by handling data: definition of data-domains,  operations on  data-domains, and data transfer. These architectures and the safety properties they ensure can be composed.
We then illustrate how to verify the properties of the architectures in an SMT solver; this is relying on an encoding into an intermediate model called pNets that already supports SMT-based verification. Additionally, the translation into  the open pNet semantic
  model gives us a strong insight on the  coordination mechanisms existing in the two models and their comparison. The approach is illustrated by a case-study where key safety properties are verified.

\keywords{Parametrised verification, composition, safety, interaction models.}
\end{abstract}
